---
title: "Quickstart"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
# The code needs the Zotero API, so it is not run when the vignette is built.
# The output shown was produced with the public group 4937409.
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

`zotFunc` downloads complete Zotero group libraries and keeps the local copies
up to date. This page covers the two calls you need most. See
`vignette("detailed-usage")` for everything else.

```{r}
library(zotFunc)
```

## Download a group

Every Zotero group has a numeric id. It is the number in the group's URL, for
example `https://www.zotero.org/groups/4937409/nature_futures_framework`.

```{r}
get_group(4937409, path = "nff", output_format = "bibtex")
#> Downloading 100 records starting at record 0 from ? ...
#> Downloading 100 records starting at record 100 from 374 ...
#> Downloading 100 records starting at record 200 from 374 ...
#> Downloading 100 records starting at record 300 from 374 ...
#> [1] "nff"
```

The total (`374`) is only known after the first response, so the first line
shows `?`.

The folder now holds one file per 100 records, plus four files describing the
download:

```{r}
list.files("nff", all.files = TRUE, no.. = TRUE)
#> [1] ".format"        ".id"            ".name"          ".version"
#> [5] "bibtex_0.bib"   "bibtex_100.bib" "bibtex_200.bib" "bibtex_300.bib"
```

## Update it

The folder knows its group and format, so the folder is all you need. Nothing
is downloaded unless the group changed on the server:

```{r}
get_group(path = "nff")
#> Group 4937409 in `nff` is up to date - nothing downloaded.
#> [1] "nff"
```

Run this as often as you like, for example in a scheduled script.
